Hydrodynamics of a Semipermeable Inextensible Membrane Under Flow and Confinement

### 2021-05-20 vesicle_code/docs/permeableVes/Response2Refs.tex
fixed a few typos

\noindent
{\bf Response:}: We thank the referee for this point. In our
    formulation, the permeation flux is proportional to the hydrostatic
    pressure and the normal component of the membrane force, which is
    the capillary pressure due to the Lagrange multiplier tension. The
    tangential force component due to tension field does not contribute
    to the permeation flux. To elucidate the relative contribution
    between the hydrostatic pressure and the normal component of the
    membrane force, we have conducted computations and added a short
    paragraph to illustrate the relative contributions in all cases.

@@

\noindent
{\bf Response:}: We have mislabeled the $Ca_E$ in Figure 5:  $Ca_E=10^0$
for the solid curves and the $Ca_E=10$ for the dashed curves. To address
the effect of Capillary number on the relaxation of a semipermeable
vesicle, we have continued the simulations for the cases of $Ca_E = 10$
much further to better illustrate the evolution of reduced area towards
equilibrium.

@@

\noindent
{\bf Response:}: The shapes along the blue curve in Figure 7(b) are
equilibrium shapes that enclose a constant area but with an efflux
(blue) and an influx (red) that adds to zero. Inset (c) illustrates the
evolution from initial  the configuration (I) to the equilibrium (shape
III), which corresponds to the case with the largest displacement on the
blue curve. To better present all these results, we have taken out the
insets (c) and (d) and moved them to the new Figure 7(a) and (b). The
new Figure 7(c) and (d) are the old Figure 7(a) and (b).

@@

\noindent
{\bf Response:}:  We have added new computations to illustrate the relative contributions of membrane tension and bending forces to the permeating fluxes for all cases in \S IV and \S V (see {\bf Response} to the second point), see the new Figures 9, 11, and 13.

@@

We thank the referee for his/her assessment of our work.  
The following is
our response to each of the specific comments and suggestions.

@@

\noindent
{\bf Response:}: The referee is correct that numerical simulations of
    two-dimensional fluid flow could be ideal and the connection to the
    real experiments is qualitative at best. The studies of
    two-dimensional vesicle hydrodynamics, however, have shown that the
    connection to real experiments or 3D simulations could be more than
    purely qualitative. For example, for a vesicle in a planar shear
    flow, the transition from tank-treading to tumbling is predicted in
    both 2- and 3-dimensions, at similar viscosity contrast. Ghiliotti,
    Biben, and Misbah (JFM, 2010) showed that results for a
    two-dimensional vesicle could be corrected systematically to agree
    with the three-dimensional results. More recently, the
    two-dimensional results in Zhang, Shen, Hogan, Barakat, and Misbah
    are also in more than qualitative agreement with real experiments
    (Biophys.~J, 2018).

>>>>

\noindent
{\bf Response:} We thank the referee for this point. In our
    formulation, the permeation flux is proportional to the hydrostatic
    pressure and the normal component of the membrane force, which is
    the capillary pressure due to the Lagrange multiplier tension. The
    tangential force component due to tension field does not contribute
    to the permeation flux. To elucidate the relative contribution
    between the hydrostatic pressure and the normal component of the
    membrane force, we have conducted computations and added a short
    paragraph to illustrate the relative contributions in all cases.

@@

\noindent
{\bf Response:} We have mislabeled the $Ca_E$ in Figure 5:  $Ca_E=10^0$
for the solid curves and the $Ca_E=10$ for the dashed curves. To address
the effect of Capillary number on the relaxation of a semipermeable
vesicle, we have continued the simulations for the cases of $Ca_E = 10$
much further to better illustrate the evolution of reduced area towards
equilibrium.

@@

\noindent
{\bf Response:} The shapes along the blue curve in Figure 7(b) are
equilibrium shapes that enclose a constant area but with an efflux
(blue) and an influx (red) that adds to zero. Inset (c) illustrates the
evolution from initial  the configuration (I) to the equilibrium (shape
III), which corresponds to the case with the largest displacement on the
blue curve. To better present all these results, we have taken out the
insets (c) and (d) and moved them to the new Figure 7(a) and (b). The
new Figure 7(c) and (d) are the old Figure 7(a) and (b).

@@

\noindent
{\bf Response:}  We have added new computations to illustrate the relative contributions of membrane tension and bending forces to the permeating fluxes for all cases in \S IV and \S V (see {\bf Response} to the second point), see the new Figures 9, 11, and 13.

@@

@@

\noindent
{\bf Response:} The referee is correct that numerical simulations of
    two-dimensional fluid flow could be ideal and the connection to the
    real experiments is qualitative at best. The studies of
    two-dimensional vesicle hydrodynamics, however, have shown that the
    connection to real experiments or 3D simulations could be more than
    purely qualitative. For example, for a vesicle in a planar shear
    flow, the transition from tank-treading to tumbling is predicted in
    both 2- and 3-dimensions, at similar viscosity contrast. Ghiliotti,
    Biben, and Misbah (JFM, 2010) showed that results for a
    two-dimensional vesicle could be corrected systematically to agree
    with the three-dimensional results. More recently, the
    two-dimensional results in Zhang, Shen, Hogan, Barakat, and Misbah
    are also in more than qualitative agreement with real experiments
    (Biophys.~J, 2018).
